Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
pass abstract, S1--3

\begin{abstract}
Software debugging is difficult. Several approaches have been proposed to the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy. This paper reports the outcome of a study performed to reassess the impact of combining Dynamic Slicing (DS) with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL. We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault. Thus, we use Mozilla's Lithium engine to minimize the failing tests source files that comprise the highest scored faulty statements from the Defects4j dataset. The impact of Tandem-FL is evaluated through computing the SFL score of each fault before and after minimization. This study also reflects on the DS limitation of missing faulty statements. Our results show that adding DS to SFL improves the SFL diagnosis accuracy.\Sof{add numbers tomorrow morning after closing results}
\end{abstract}

@@

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. To sum, our
results show that \Sof{@todo: sum up the results}.

>>>>

\begin{abstract}
Several approaches have been proposed to improve automated softaware fault
diagnosis, aiming to reduce the effort and costs spent in debugging. This
paper reports the outcome of a study
performed to reassess\Rui{dismistify? We need to say something on why we
decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
suspect that several highly suspiscious components \Rui{I am using components to be
more generic} --- often involved in failing, but seldom in passed executions ---
may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
the failing tests source files that comprise the highest scored faulty
statements from the Defects4j dataset\Rui{not clear why this is in here for
the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
through computing the SFL score \Rui{SFL score: a reader does not know what that is}
of each fault before and after minimization\Rui{minimization: unknown to the
reader... He thinks that the study is on slicing}.
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that adding combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of oberved failures faster.
\end{abstract}

@@

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. Our
results show that \Sof{@todo: sum up the results}.
